### 2023-11-12 manuscript/manuscript.Rmd
Reword sentence in Section 3.2
correct sentence structure

Ultra-high resolution MS instrumentation utilising Orbitrap mass analyser technology is now commonplace in many laboratories, which can yield many thousands of *m/z* features in a single analytical run [@hu2005].
This has provided an unprecedented opportunity for metabolite annotation and has been applied to direct infusion approaches like flow infusion electrospray high-resolution MS (FIE-HRMS), commonly applied for 'first pass' metabolome fingerprinting and liquid chromatography (LC) HRMS profiling for non-targeted metabolomic analyses.
However, high mass accuracy alone is insufficient for unambiguous metabolite annotation [@kind2006].

@@

While not the intended primary application of the approach, the C18-UPHLC-HRMS data from *B. distachyon* had the highest percentage of *m/z* features assigned along with the greatest number of molecular formulas. 
The chromatographic separation of the C18-UHPLC-HRMS enables the correlation network to be considered within limited retention time windows and increases the likelihood that a number of correlated IPs will be present for a given compound.
Added to this, the LC-MS reduces the effects of ion suppression compare to FIE-HRMS and also decreases the chance of potential interference in the correlations between related features due to the presence of structural isomers and isobaric compounds [@gowda2014].

>>>>

Ultra-high resolution MS instrumentation utilising Orbitrap mass analyser technology is now commonplace in many laboratories, which can yield many thousands of *m/z* features in a single analytical run [@hu2005].
This has provided an unprecedented opportunity for metabolite annotation and has been applied to direct infusion approaches like flow infusion electrospray high-resolution MS (FIE-HRMS), commonly applied for 'first pass' metabolome fingerprinting, as well as liquid chromatography (LC) HRMS profiling for non-targeted metabolomic analyses.
However, high mass accuracy alone is insufficient for unambiguous metabolite annotation [@kind2006].

@@

The C18-UPHLC-HRMS data from *B. distachyon* had the highest percentage of *m/z* features assigned along with the greatest number of molecular formulas. 
The chromatographic separation of the C18-UHPLC-HRMS enables the correlation network to be considered within limited retention time windows and increases the likelihood that a number of correlated IPs will be present for a given compound.
Added to this, the LC-MS reduces the effects of ion suppression compare to FIE-HRMS and also decreases the chance of potential interference in the correlations between related features due to the presence of structural isomers and isobaric compounds [@gowda2014].
